On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-06-16 paper_lap/JCP_response1/01intro.tex
updating paper

\section{Introduction}
Laplace's equation arises in a vast array of contexts (electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs). As such, effective numerical methods for quickly and robustly solving Laplace's equation with high accuracy are desirable. Approaches based on potential theory proceed by reducing PDEs to second-kind boundary integral equations (BIEs), where the solution to the boundary value problem is represented by layer potentials on the boundary of the domain. Once these boundary integral equations are discretized the resulting linear systems are better-conditioned than those obtained by directly discretizing the PDE. When the boundary of the domain is smooth there are numerous methods for solving BIEs quickly and accurately (see~\cite{hao}, for example).

Near corners, however, the solutions to both the partial differential equations and corresponding boundary integral equations may have singularities, preventing the application of many traditional methods. Fortunately, a number of approaches have been developed to obviate this difficulty. One class of methods proceeds by introducing many additional degrees of freedom in the vicinity of the corners. In order to prevent the resulting linear systems from becoming intractably large one can use a variety of methods for {\it compressing} the linear system, effectively eliminating the extra degrees of freedom added in the vicinity of the corners. Moreover, the corner refinement and compression can be done in tandem resulting in fast and accurate solvers for elliptic PDEs (see \cite{helsing}, \cite{helsing2},  \cite{ojala}, \cite{helsjcp} and \cite{helsinv}  for  one approach called recursive compressed preconditioning, and  \cite{gillman}, \cite{bremer},\cite{bremer2}, and \cite{bremer3}  for other compression-based methods for solving Laplace's equation). Unfortunately, this approach becomes considerably more expensive in three dimensions limiting its application in that context.

@@

 In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on using the discretization of a suitable adjoint problem. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner.

>>>>

\section{Introduction}
Laplace's equation arises in a vast array of contexts (electrostatics, harmonic functions, low-frequency acoustics, percolation theory, homogenization theory, and the study of field enhancements in vacuum insulators for example) and serves as a useful model problem for the study of general elliptic partial differential equations (PDEs). As such, effective numerical methods for quickly and robustly solving Laplace's equation with high accuracy are desirable. Approaches based on potential theory proceed by reducing PDEs to second-kind boundary integral equations (BIEs), where the solution to the boundary value problem is represented by layer potentials on the boundary of the domain. Once these boundary integral equations are discretized the resulting linear systems are better-conditioned than those obtained by directly discretizing the PDE. When the boundary of the domain is smooth there are numerous methods for solving BIEs quickly and accurately (see~\cite{hao}, for example).

Near corners, however, the solutions to both the partial differential equations and corresponding boundary integral equations may have singularities, preventing the application of many traditional methods. Fortunately, a number of approaches have been developed to obviate this difficulty. One class of methods proceeds by introducing many additional degrees of freedom in the vicinity of the corners. In order to prevent the resulting linear systems from becoming intractably large one can use a variety of methods for {\it compressing} the linear system, effectively eliminating the extra degrees of freedom added in the vicinity of the corners. Moreover, the corner refinement and compression can be done in tandem resulting in fast and accurate solvers for elliptic PDEs (see \cite{helsing}, \cite{helsing2},  \cite{ojala}, \cite{helsjcp} and \cite{helsinv}  for  one approach called recursive compressed preconditioning, and  \cite{gillman}, \cite{bremer},\cite{bremer2}, and \cite{bremer3}  for other compression-based methods for solving Laplace's equation). Unfortunately, this approach becomes considerably more expensive in three dimensions.

@@

 In this paper we describe a method for solving Laplace's equation on polygonal domains with Neumann boundary conditions given only a discretization of a corresponding Dirichlet problem. Our approach is based on using the discretization of a suitable adjoint problem. In particular, we show that if the transpose of the discretization of a suitable Dirichlet BIE is used, then the resulting solution will be accurate in a ``weak sense''; namely, it can be used to compute inner products with smooth functions accurately, though it cannot be interpolated. We then show how this solution can be used to obtain accurate solutions to the Neumann problem arbitrarily close to a corner by solving a set of local subproblems in the vicinity of that corner. \upd{This approach generalizes naturally to three-dimensional problems, though efficient discretization of the corresponding Dirichlet problems is the subject of ongoing research. A similar analysis as in \cite{} can be used to characterize the singularities along edges and near vertices, though there are a few challenges which prevent the immediate application of this analysis to the design of suitable discretizations.}

### 2020-06-16 paper_lap/JCP_response1/03bvp.tex
updating paper

 \section{Boundary integral equations \label{sec:bvp}}
A classical technique for solving the four Laplace boundary value problems given above is to reduce them to boundary integral equations. Before describing this procedure we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}\label{def_layerpots}
Given a function $\sigma:\Gamma \to \mathbb{R}$, the single-layer potential is defined by
\beqn
\cS[\sigma](\by) =  \int_{\Gamma} G (\bx,\by)\sigma(\bx) {\rm d}S_{\bx} \, ,
\eeqn
where
\beqn
G(\bx,\by) = -\frac{1}{2\pi} \log{|\bx-\by|}.
\eeqn
Similarly, the double-layer potential is defined via the formula
\beqn
\cD[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by) \sigma(\bx) {\rm d}S_{\bx}.
\eeqn
\end{definition}
In the following we will often refer to the function $\sigma$ as the {\it density} which generates the corresponding potential.
\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K(\bx,\by)$ by
\begin{equation}
K(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by),
\end{equation}
where $\bnu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
work instead with a parametrization of $K.$ In particular, if $\gamma :[0,L] \to \Gamma$ is a counterclockwise 
arclength parametrization of $\Gamma,$ 
we denote by $k:[0,L]\times [0,L] \to \mathbb{R}$ the function defined by
\begin{align}
k(s,t) = K(\gamma(s),\gamma(t)).
\end{align}
{\color{olive}By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
\end{definition}

@@

\begin{theorem}\label{thm:potlim}
Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ (where $\bx_{0}$ is not a corner vertex) from the inside along a path such that 
\begin{align}
-1+\alpha<\frac{\bx-\bx_0}{\|\bx-\bx_0\|} \cdot \gamma'(t_0) <1-\alpha
\end{align}
for some $\alpha >0.$ Then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
{\color{olive}
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)- \frac{\sigma(\bx_0)}{2}\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0^+}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))+ \frac{\sigma(\bx_0)}{2},
\end{align}
where $\bnu$ is the inward-pointing normal.} Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
{\color{olive}
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)+ \frac{\sigma(\bx_0)}{2}\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0^+}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))- \frac{\sigma(\bx_0)}{2}.
\end{align}}
\end{theorem}

Next we define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}\label{def_singder}
Let $\cS$ be the single-layer potential operator and $\bnu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\bx_0 \in \Gamma,$
\begin{align}
\bnu(\bx_0)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)).
\end{align}
{\color{red}where $\gamma(t_0) = \bx_0.$}
\end{definition}

@@

\begin{remark1}
A similar result holds for the case where the identity term in (\ref{eqn_grho}) is replaced by its negative; the change in sign corresponds to replacing the boundary integral equation for the interior Dirichlet problem with the boundary integral equation corresponding to exterior Dirichlet problem. Similar expansions also hold for both the exterior and interior Neumann problems, in which case the singular powers are obtained by subtracting one from the singular powers arising in the Dirichlet problem.
\end{remark1}

{\color{olive}
\begin{remark1}
We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{} for example.
\end{remark1}
}

>>>>

 \section{Boundary integral equations \label{sec:bvp}}
A classical technique for solving the four Laplace boundary value problems given above is to reduce them to boundary integral equations. Before describing this procedure we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}\label{def_layerpots}
Given a function $\sigma:\Gamma \to \mathbb{R}$, the single-layer potential is defined by
\beqn
\cS[\sigma](\by) =  \int_{\Gamma} G (\bx,\by)\sigma(\bx) {\rm d}S_{\bx} \, ,
\eeqn
where
\beqn
G(\bx,\by) = -\frac{1}{2\pi} \log{|\bx-\by|}.
\eeqn
Similarly, the double-layer potential is defined via the formula
\beqn
\cD[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by) \sigma(\bx) {\rm d}S_{\bx}.
\eeqn
\end{definition}
In the following we will often refer to the function $\sigma$ as the {\it density} which generates the corresponding potential.
\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K(\bx,\by)$ by
\begin{equation}
K(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G(\bx,\by),
\end{equation}
where $\bnu(\bx)$ is the inward-pointing normal to $\Gamma$ at $\bx.$ It will often be convenient to 
work instead with a parametrization of $K.$ In particular, if $\gamma :[0,L] \to \Gamma$ is a counterclockwise 
arclength parametrization of $\Gamma,$ 
we denote by $k:[0,L]\times [0,L] \to \mathbb{R}$ the function defined by
\begin{align}
k(s,t) = K(\gamma(s),\gamma(t)).
\end{align}
\upd{By a standard abuse of notation we use $\cS$ and $\cD$ to denote both the operators acting on $L^2(\Gamma)$ as well as the corresponding operators acting on $L^2([0,L]),$ the latter being obtained from the former by composition with the parameterization.}
\end{definition}

@@

\begin{theorem}\label{thm:potlim}
Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ (where $\bx_{0}$ is not a corner vertex) from the inside along a path such that 
\begin{align}
-1+\alpha<\frac{\bx-\bx_0}{\|\bx-\bx_0\|} \cdot \gamma'(t_0) <1-\alpha
\end{align}
for some $\alpha >0.$ Then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
\upd{
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)- \frac{\sigma(\bx_0)}{2}\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0^+}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))+ \frac{\sigma(\bx_0)}{2},
\end{align}
where $\bnu$ is the inward-pointing normal.} Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then for any continuous function $\sigma:\Gamma \to \mathbb{R},$
\upd{
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\sigma](\bx) = \cD[\sigma](\bx_0)+ \frac{\sigma(\bx_0)}{2}\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\sigma](\bx+\tau \bnu(\bx_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0^+}\cS[\sigma](\bx_0+\tau \bnu(\bx_0))- \frac{\sigma(\bx_0)}{2}.
\end{align}}
\end{theorem}

Next we define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}\label{def_singder}
Let $\cS$ be the single-layer potential operator and $\bnu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\bx_0 \in \Gamma,$
\begin{align}
\bnu(\bx_0)\cdot \nabla \cS[\rho] (\bx_0) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\bx_0 + \tau \bnu(\bx_0)).
\end{align}
\end{definition}

@@

\begin{remark}
A similar result holds for the case where the identity term in (\ref{eqn_grho}) is replaced by its negative; the change in sign corresponds to replacing the boundary integral equation for the interior Dirichlet problem with the boundary integral equation corresponding to exterior Dirichlet problem. Similar expansions also hold for both the exterior and interior Neumann problems, in which case the singular powers are obtained by subtracting one from the singular powers arising in the Dirichlet problem.
\end{remark}

\upd{
\begin{remark}
We note that the smoothness of the kernel $k$ for well-separated portions of the domain guarantees that the problem of determining the singularities arising in the vicinity of a corner for a polygonal domain can be reduced to the analysis of the wedge case, see the discussion in \cite{} for example.
\end{remark}
}

### 2020-06-16 paper_lap/JCP_response1/04nprelim.tex
updating paper

The Nystr\"{o}m method proceeds as follows. We begin by constructing a discretization of the boundary $\Gamma$ with nodes {\color{blue}$x_1,\dots,x_N,$} and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}\label{eqn:numpreint}
f(s) = -\frac{\sigma(s)}{2} + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ In other words, given {\color{blue}$f(x_i),-\sigma(x_i) + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$

Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
{\color{blue}
\begin{align}
f(x_i) \sqrt{w_i} = -\frac{\sigma(x_i)\sqrt{w_i}}{2} +  \sqrt{w_i}\int_0^L k(t,x_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
\end{align}
}
We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}. The new unknowns are $\sigma_i = \sigma({\color{blue}x_i}) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node {\color{blue}$x_i$} we find a collection of weights $W_{ij}$ such that
\begin{align}
\left|\int_0^L k(t,{\color{blue}x_i})\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
\end{align}
resulting in the linear system
\begin{align}
  -\frac{\sigma_i}{2} +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f({\color{blue}x_i}) \sqrt{w_i},\quad i,j=1,\dots,N. 
\end{align}

@@

The boundary $\Gamma$ is separated into a collection of intervals which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner and the collection of intervals of length $2 \delta$ centered about each corner. The former are discretized using a standard smooth quadrature rule such as nested Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.

First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized using nested Gauss-Legendre panels in $x$ and a single Gauss-Legendre panel in $\mu$. This creates a $N \times M$ matrix where $N$ denotes the number of spatial discretization points $r_i$ and $M$ denotes the number of $\mu_j$ chosen. $M$ and $N$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range. A singular value decomposition is then performed on the $N\times M$ matrix. Let $K$ denote the number of singular values greater than $\epsilon.$ The right singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$

Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{w_j}$ is well-conditioned. In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system. The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$

@@

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,\upd{x_j}) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
\begin{remark1}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^1 k(t,-x_j) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_j$ was one of the original discretization nodes generated on the interval $[0,1].$
\end{remark1}
\begin{remark1}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,\upd{x_i}) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{\upd{i,j}} \tilde{\phi}_{m}(\upd{x_j}) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark1}

After all the quadratures have been constructed the result is an $N \times N$ linear system the solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.

@@

The results of this algorithm are summarized in the following theorem (see \cite{}).
\upd{
\begin{theorem}
Let $A$ the integral operator corresponding to the interior Dirichlet problem, i.e. 
\begin{equation}
A[\sigma](s) = -\frac{\sigma(s)}{2} + \int_{0}^{L} k(t,s) \sigma(t) dt \, . 
\end{equation}
Let $\uA \in \mathbb{R}^{N\times N}$ denote the corresponding discretized matrix. In particular if $f \in S_\epsilon $ is piecewise analytic and 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, ,
\end{equation}
then
\begin{align}
\underline{\sigma} = \uA^{-1} {\uf}
\end{align}
can be interpolated to a function $\tilde{\sigma}$ which is within $\epsilon$ of the true density $\sigma$ in an $L^2$-sense. 
\end{theorem}
}

@@

>>>>

The Nystr\"{o}m method proceeds as follows. We begin by constructing a discretization of the boundary $\Gamma$ with nodes \upd{$x_1,\dots,x_N,$} and weights $w_1,\dots,w_N,$ which enable interpolation of the left- and right-hand sides of the boundary integral equation
\begin{align}\label{eqn:numpreint}
f(s) = -\frac{\sigma(s)}{2} + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t
\end{align}
with precision $\epsilon.$ In other words, given \upd{$f(x_i),$ and $-\sigma(x_i)/2 + \int_0^L k(t,x_i) \,\sigma(t)\, {\rm d} t,$} for $i=1,\dots,N,$ the values $f(s)$ and $-\sigma(s)/2 + \int_0^L k(t,s) \,\sigma(t)\, {\rm d} t$ can be obtained for all $0 \le s \le L$ to within $\epsilon.$

Once these nodes and weights have been generated we proceed by enforcing equality of (\ref{eqn:numpreint}) at the discretization nodes, which yields the system of equations
\upd{
\begin{align}
f(x_i) \sqrt{w_i} = -\frac{\sigma(x_i)\sqrt{w_i}}{2} +  \sqrt{w_i}\int_0^L k(t,x_i)\, \sigma(t)\,{\rm d}t,\quad i=1,\dots,N. \label{eqn_1std}
\end{align}
}
We note that scaling by the square root of the weights in the above equation is equivalent to solving the problem in the $L^2$ sense, and results in discretized operators with condition numbers which are close to those of the original physical systems \cite{bremer3}. The new unknowns are $\sigma_i = \sigma(\upd{x_i}) \sqrt{w_i},$ $i=1,\dots,N.$ Next, for each interpolation node \upd{$x_i$} we find a collection of weights $W_{ij}$ such that
\begin{align}
\left|\int_0^L k(t,\upd{x_i})\, \sigma(t)\,{\rm d}t- \sum_{j=1}^N W_{ij} \sigma_j\, \sqrt{w_j} \right| < \epsilon,
\end{align}
resulting in the linear system
\begin{align}
  -\frac{\sigma_i}{2} +  \sum_{j=1}^N W_{ij} \sigma_j \sqrt{w_i w_j}=f(\upd{x_i}) \sqrt{w_i},\quad i,j=1,\dots,N. 
\end{align}

@@

The boundary \upd{$\Gamma$ is divided into a collection of disjoint pieces each of which are at least a fixed distance $\delta$  (measured in terms of arclength) away from a corner, and a collection of pieces of length $2 \delta$ centered about each corner. }The former are discretized using a standard smooth quadrature rule such as Gauss-Legendre quadrature while the latter are discretized using a custom set of interpolation nodes constructed in the following way.

First, all functions of the form $x^\mu,$ $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1]$ are discretized \upd{ in $x$ using an adaptive interpolation scheme based on Gauss-Legendre panels}, and \upd{in $\mu$ using} a single Gauss-Legendre panel for the range $[1/2,50].$ This creates a $N_x \times (N_\mu+1)$ matrix where $N_x$ denotes the number of spatial discretization points $r_i$ and $N_\mu$ denotes the number of $\mu_j$ chosen. The extra row in the matrix corresponds to the special case when $\mu = 0.$ $N_x$ and $N_\mu$ are increased until it is guaranteed that using Lagrange interpolation from the nested discretization the function $x^\mu$ can be interpolated to within an $L^2$ error less than $\epsilon$ on the interval $[0,1]$ for any $\mu$ in the specified range. A singular value decomposition is then performed on the $N_x \times (N_\mu+1)$ matrix. Let $K$ denote the number of singular values greater than $\epsilon.$ The left singular vectors correspond to discretizations of an orthonormal set of functions $\phi_1,\dots,\phi_K$ such that $x^\mu$ is in the span of $\phi_1,\dots,\phi_K$ to within an accuracy of $\epsilon.$

Finally, a set of interpolation points $x_j,$ $j=1,\dots,K$ and quadrature weights $w_j,$ $j=1,\dots,K$ are chosen for $\phi_1,\dots,\phi_K$ such that the matrix $U_{ij} = \phi_i(x_j) \sqrt{w_j}$ is well-conditioned. In practice suitable interpolation points can be obtained by using the roots of $\phi_{K+1}$ and calculating the corresponding weights by solving a linear system. The corresponding discretization nodes and weights for the corner-containing intervals of $\Gamma$ are obtained by suitable translations and scalings of $\{x_j\}$ and $\{w_j\}.$ \upd{We note that in practice, to achieve an accuracy of $10^{-15}$ for all powers $\mu \in \{0\} \cup [1/2,50],$ $x \in [0,1],$ only about $36$ nodes are required (i.e. $K = 36$).}

@@

Once the discretization has been constructed it is necessary to construct appropriate quadrature for the integrals appearing in equation (\ref{eqn_1std}). When \upd{$x_i$} and $t$ do not belong to the same corner panel (in particular when either is not itself contained in a corner panel) then the weights and nodes associated with the discretization can be used as the quadrature rule. When $s_i$ corresponds to a corner panel special care must be taken. Instead, using an algorithm for generating generalized Gaussian quadratures \cite{bremer2010}, quadrature nodes are chosen which integrate
\begin{align}
\int_{0}^\delta k(t,\upd{x_i}) \tilde{\phi}_j(t)\,{\rm d}t
\end{align} 
where $\tilde{\phi}_j$ is a suitably scaled and translated copy of the singular function obtained in the discretization step, and for ease of exposition we assume that the corner panel corresponds to $(-\delta,\delta)$ in the parametrization with $t=0$ corresponding to the corner itself. Moreover, in light of symmetry between the two legs of the wedge it suffices to design quadratures assuming  \upd{$x_j$} lies in the half of a corner panel parametrized by $(-\delta,0).$
\begin{remark}
Due to scale invariance, it suffices to compute quadratures for 
\begin{align}
\int_{0}^1 k(t,-x_i) {\phi}_j(t)\,{\rm d}t,
\end{align} 
where $x_i$ was one of the original discretization nodes generated on the interval $[0,1].$
\end{remark}
\begin{remark}
By interpolating from the discretization nodes to these quadrature nodes we obtain a set of weights $\tilde{W}_{i,j}$ such that if \upd{$x_1,\dots,x_{2K}$} correspond to the discretization of a corner parametrized by $(-\delta,\delta)$ with $0$ corresponding to the corner then
\begin{align}
\left| \int_{-\delta}^\delta k(t,\upd{x_i}) \, \tilde{\phi}_m(t)\,{\rm d}t - \sum_{j=1}^{2K} \tilde{W}_{\upd{i,j}} \tilde{\phi}_{m}(\upd{x_j}) \right| < \epsilon
\end{align}
for all $i=1,\dots,2K$ and $m=1,\dots,K.$
\end{remark}

After all the quadratures have been constructed the result is an $N \times N$ linear system the \upd{scaled} solution of which gives an approximation to $\sigma$ sampled at the discretization nodes.

@@

The results of this algorithm are summarized in the following theorem (see \cite{hoskins2019numerical}).
\upd{
\begin{theorem}
Let $A$ denote the integral operator corresponding to the interior Dirichlet problem, i.e. 
\begin{equation}
A[\sigma](s) = -\frac{\sigma(s)}{2} + \int_{0}^{L} k(t,s) \sigma(t) dt \, . 
\end{equation}
Let $\uA \in \mathbb{R}^{N\times N}$ denote the corresponding discretized matrix. In particular if $f \in S_\epsilon $ is piecewise analytic and 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, ,
\end{equation}
then, after a suitable rescaling,
\begin{align}
\underline{\sigma} = \uA^{-1} {\uf}
\end{align}
can be interpolated to a function $\tilde{\sigma}$ which is within $\epsilon$ of the true density $\sigma$ in an $L^2$-sense. 
\end{theorem}
}

@@

\upd{For ease of exposition, here we describe the exterior Neumann problem though an identical procedure can be used for the interior Neumann problem. In the latter case it is well-known that the naive boundary integral equation formulation has a one-dimensional nullspace (corresponding to the fact that solutions to the corresponding PDE are unique only up to a constant). Using standard techniques (see \cite{} for example) this issue can be corrected and the method of this paper can be applied in a straightforward manner.}
